Questions to Developers

### 2021-07-14 StateOfPractice/Ao-Notes/DomainExptMeeting/Presentation for the Introductory Meeting.tex
Add goal to ranking follo-up slide
Updates to domain expert meeting slides

\bi
\item \structure{Can you review the full ranking measurements?}
\bi
\item There are 9 measurements
\item The write up is about 10 pages long \ei \ei

@@

\begin{frame}
\frametitle{Pain Points from Developer Interviews}

\structure{Do these fit with your experience?}
\bi
\item Lack of time to 1) implement all requested new features 2) write and maintain good documents 3) review all contributions from the community
\item It is difficult to find or keep the members with experience in both software development and medical imaging
\item Lack of funding for software development (especially for maintenance)
\item No organizations to help with developing high quality software
\item Difficulty to get test data
\item Difficulty to achieve cross-platform compatibility: 1) native app - more time and work 2) web app w/o server - worse performance 3) web app w/ servers - more cost
\ei

@@

\structure{Do these seem feasible?  What other ideas do we have?}
\bi
\item Consult with software development organization
  \bi
\item Better Scientific Software (BSSw)
\item Software Sustainability Institute
\item Software Carpentry
  \ei
\item Citations for software (Katz project)
  \item Redefine productivity to include time working on tasks like testing, continuous
    integration and documentation
\ei

@@

\bi
\item \structure{What experience do you, or your students, have with developing
    software?}
\item \structure{How big would the development group be?}
\item \structure{What is the typical background of a developer?}
\item \structure{How many users would you software typically have?}
\item \structure{What is the typical background of a user?}
\item \structure{Currently, what are the most significant obstacles in your
    development process?}
\item \structure{How might you change your development process to remove or
    reduce these obstacles?}
\item \structure{How does documentation fit into your development process? Would improved
  documentation help with the obstacles you typically face?}      
\ei

>>>>

\bi
\item \structure{Can you review the full ranking measurements?}
\bi
\item There are 9 measurements
\item The write up is about 10 pages long
\item Our goal is to find anything that seems out of place
  \ei \ei

@@

\begin{frame}
\frametitle{Developer Interviews: Pain Points}

\be
\item Lack of time to 1) implement all requested new features 2) write and
  maintain good documents 3) review all contributions from the community
\item It is difficult to find or keep the members with experience in both
  software development and medical imaging
\item Lack of funding for software development (especially for maintenance)
\item No organizations to help with developing high quality software \label{NoOrg}
\item Difficulty to get test data
\item Difficulty to achieve cross-platform compatibility: 1) native app - more
  time and work 2) web app w/o server - worse performance 3) web app w/ servers
  - more cost \ee

@@

\structure{Do these seem feasible?  What other ideas do we have?}
\bi
\item Consult with software development organization (P\ref{NoOrg})
  \bi
\item Better Scientific Software (BSSw)
\item Software Sustainability Institute
\item Software Carpentry
  \ei
\item Citations for software (Katz project)
  \item Redefine productivity to include time working on tasks like testing, continuous
    integration and documentation
\ei

@@

\bi
\item \structure{What experience do you, or your students, have with developing
    software?}
\item \structure{How big would the development group be?}
\item \structure{What is the typical background of a developer?}
\item \structure{How many users would your software typically have?}
\item \structure{What is the typical background of a user?}
\item \structure{Currently, what are the most significant obstacles in your
    development process?}
\item \structure{How might you change your development process to remove or
    reduce these obstacles?}
\item \structure{How does documentation fit into your development process? Would improved
  documentation help with the obstacles you typically face?}      
\ei
